---
title: "DVC Example"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## install
```{r}
devtools::install_github("git@github.com:insilica/dvcr.git")
library(dvcr)
```
## Adding files to track locally with dvcr

You can't have a `data` dir and track all files with `dvcr::add("data")` for a project if you also want to `dvcr::import` into that dir at a later time to track remote files. You have to stick to using `dvcr::add` on just individual files that live in a `data` dir as opposed to adding whole directories at a time. If you try to add a `data` dir locally then try to `dvcr::import` another file into the `data` dir, it will break the dvc dir structure setup with .gitignore

Succintly, only `dvcr::add` and `dvcr::import` individual files, not whole dirs. You may (and probably should) import remote files into subdirs, e.g. `data/pharmgkb/relationships.Rdata`. 

```{r}
data_dir <- here::here("data")
dir.create(data_dir)
cars_filename <- file.path(data_dir,"cars.txt")
save(cars,file=cars_filename)

# be sure to have dvc installed

# this should fail, but is left as example
dvcr::use_dvc()
dvcr::add(path=cars_filename)

```

You should also commit the data.dvc file generated
```{r}
git2r::add(path=file.path(data_dir,"cars.txt.dvc"))
```

```{r}
# this will also fail, but kept as example
dvcr::remote_add(name = "s3", url = "s3://ins-dvc/ins-dvc-example")
s3_remote = "s3"
push(remote=s3_remote)

# if this was the first time you downloaded the repo, you could do a
pull()
```

## Get files
This will place relationships.Rdata into data/pharmgkb
```{r}
pharmgkb_dir = file.path(data_dir,"pharmgkb")
dir.create(pharmgkb_dir)
dvcr::get("git@github.com:insilica/pharmgkb-dvc.git","data/relationships.Rdata",out=pharmgkb_dir)
```

## import files
Get will only place the file into your `data` dir and will not track it

```{r}
dvcr::import(url="git@github.com:insilica/pharmgkb-dvc.git",path="data/relationships.Rdata",out=pharmgkb_dir)
```

We now have the data, we can add it to our repo to be tracked by dvc
```{r}
git2r::add(path=pharmgkb_dir)
```

